%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Fullstack Software Engineer} % Job title
    {ZALORA Group} % Organization
    {Ho Chi Minh City} % Location
    {10/2019 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Owning, maintaining and developing features for Zalora website on mobile devices in 6 countries.}
        \item {Working with state-of-the-art search engine in order to ensure that every search query in Zalora delivering meaningful and helpful results for customers.}
      \end{cvitems}
    }
     \cventry
    {Lite (web mobile)} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Released Earth Edit and Luxury and they are contributed to 15 \% of total ZALORA Q3 2020}
        \item {Optimized service worker so that it worked for 6 countries and for 3 environments (instance/staging/production) without conflicting}
        \item {Moved building process from Jenkins to AWS Codebuild}
        \item {Rewrited Proxy to enable easy development from any environments}
        \item {Optimized/Filtered noise in error logs in Sentry}
        \item {Optimized bundle size under 150KB for main and 32KB for other chunks}
        \item {Added/Fixed proper eslint rule for the whole project}
        \item{Optimized building/deploying pipeline for releasing to production}
        \item {Built bot instance with AWS Serverless to helps deploying ticket easily to instance environment}
      \end{cvitems}
    }
    
     \cventry
    {Costa} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported A/B testing for Learning to Ranks with Solr, third party Datajet, and many other features}
        \item {Reduced error rate on Newrelic to less than 1\%}
        \item {Helped to improve caching with in-memory}
        \item {Moved Costa architecture from in-place deployment EC2 to ECS blue-green deployment}
        \item {Supported to refine errors and logging in Newrelic and Sentry}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Software Engineer \& Scrum Guardian} % Job title
    {DEK Technology} % Organization
    {Ho Chi Minh city} % Location
    {04/2018 -- 10/2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped Scrum master to facilitate team, and came up with a solution to improve team performance}
        \item {Maintained and developed feature for Davis, a visualization tool helping people to have a statistic view of test cases executed by Jenkins.  }
        \item {Launched and built Kafka connectors to actively pull the result from Jenkins using XPATH selectors and send the records to a Kafka cluster by interval.}
        \item {Researched optimizing backend data query time using hadoop HDFS + Apache Hive and compared with Cassandra.}
        \item {Deployed Kafka Confluence and Davis application (frontend + backend) to the provided Kubernetes cloud service.}
        \item {Developed a Logging system from a local machine using EFK stack (Elasticsearch, FluentD, Kibana), deployed also in Kubernetes}
        \item {Set up CI system using Jenkins and Gerrit and improve coverage of the source connector project to nearly 100\% by refactoring project structure and adding Unit tests}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Fresher} % Job title
    {Global Cybersoft} % Organization
    {Ho Chi Minh city} % Location
    {07/2017 -- 04/2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and developed new features for the desktop application project helping to operate industrial printing machines using Java Swing.}
        \item {Drew a design diagram, writing test cases, fixed bugs on development tracks, and customer’s requests.}
        \item{Worked closely with SE,QA,PM to resolve issues raised by customers asap.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer Intern} % Job title
    {} % Organization
    {} % Location
    {06/2016 -- 12/2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the surveillance system using Spring MVC framework in combination with Hibernate and PostgreSQL. The system will display recorded images from the camera after running them through the CV algorithm}
        \item {Worked as the core member of the team and helped to build the project structure from the beginning.}
        \item{Presented the demo of the project to stakeholders and clients by the end of each sprint.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
