%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Pet Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Frontend} % Job title
    {DeKal Portfolio} % Organization
    {Ho Chi Minh} % Location
    {11/2019 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Built my portfolio project from scratch using the cutting-edge framework Nextjs.}
         \item[] {\it Tech Stack: Nextjs, DangerJS, CircleCI, Vercel, Lighthouse, Scrutinizer}
        \item {Configured app deployment with Vercel.}
        \item {Configured CI/CD pipeline with Github, DangerJS, Vercel, CircleCI, and Scrutinizer}
        \item {Configured performance CI tool with LightHouse. The performance test will run on opening/updating a pull request.}
        \item {Adding simple release mechanism and CHANGLOG.md to track the versions.}
        \item {Visit my page at \it \href{https://phatho-folio.now.sh/}{here}. }
      \end{cvitems}
    }

    \cventry
    {Backend + CMS} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an api backend using Spring MVC Framework allows frontend to fetch neccessary configs and blogs from MongoDB.}
        \item[] {\it Tech Stack: Spring MVC, Java, DangerJS, CircleCI, Heroku, Swagger, Codecov, Gradle, React CRA, Redux, MongoDB}
        \item {Integrated a CMS frontend to allow users to easily do modifications/add/update data.}
        \item {Built mechanism to include CMS frontend bundle from Reactjs into static resources to serve with Spring MVC.}
        \item {Deployed using Heroku pipeline Review - Staging - Production.}
        \item {Configured CI/CD pipeline with Github, DangerJS, CircleCI, Heroku, and Codecov.}
        \item {Built a release script with net.researchgate.release and Git Changelog Gradle.}
        \item {Setup Swagger to document apis. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tech Lead \& Scrum Master} % Job title
    {Boot Career} % Organization
    {United State} % Location
    {08/2020 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Re-architect the old application with ReactJS and refactor it to better project structure with Redux ToolKit.}
        \item {Defined team rituals, team working process on tech side and way of workings following Agile Scrum.}
        \item {Splitting tasks by features and coordinating members to work on it.}
        \item {Helped to refine the working process and removed impediments. }
      \end{cvitems}
    }

 \cventry
    {Jobseeker Dashboard} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {A web application for helping people from non-traditional backgrounds and underrepresented communities get jobs in tech}
        \item[] {\it Tech Stack: React CRA, Redux Toolkit, Storybook, eslint, lerna, React Testing library, CircleCI, Netlify}
        \item {Re-architect the old application with ReactJS and refactor it to better project structure with Redux ToolKit.}
        \item {Broke down the design part by part and coordinated team members to do the task.}
        \item {Setup CI/CD with Circle CI, Eslist, and Netlify.}
        \item {Setup a storybook, to isolate components for independently development.}
        \item {Built a proper project structure based module and good global state management flow.}
        \item {Built a release pipeline with CHANGLOG and github tags.}
      \end{cvitems}
    }
    
\cventry
    {User Service} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A Nodejs Application to store data of candidate and user signing up to the system.}
        \item[] {\it Tech Stack: Typescript, Nodejs, Express, Toolkit, Eslint, Terraform, Github action, Heroku, MongoDB}
        \item {Re-architect and convert the whole application built with Nodejs Express Framework from Javascript to Typescript.}
        \item {Integrated Swagger with the backend service.}
        \item {Setup CI/CD with Github action, Eslist, and Heroku pipeline.}
        \item {Built a new project using terraform to manage the infrastructure of the whole organization (Infrastructure as Code).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {Popswap} % Organization
    {Sweden} % Location
    {06/2020 -- 09/2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained the application allowing people to swipe for swapping clothes and items like Tinder.}
        \item[] {\it Tech Stack: React Native, Redux, Android, IOS}
        \item {Refactored/redesigned the application with new looks.}
        \item {Restructure the structure of the React Native application, adds new scripts to deploy, remove tricky hack of the old owner and create a smooth environment for development.}
        \item {Removed old/stale features that existed in the application.}
        \item {Added integration with swish bank and developed new premium features with Google and Apple store. }
      \end{cvitems}
    }
    

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Live Guess} % Organization
    {Ho Chi Minh city} % Location
    {3/2019 -- 5/2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a system to allow users guessing based on  events using ReactJS.}
        \item[] {\it Tech Stack: ReactJS, Webpack, Redux, Docker, Apache Cordorva}
        \item {Use long-polling to sync events continuously with the current time.}
        \item{Create the UI with interactive timer and lively interaction.}
        \item{Used Cordorva to build an application version based on the web mobile app for android}
        \item {Built docker container to deploy directly on Client server}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
